Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-08 paper/paper.tex
No applications of strongly connected

For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
undirected). For directed graphs, there is more than one notion of connectivity, and it is not clear
which should be selected---the approaches we consider extend easily to weakly connected directed
graphs, but not to the strongly connected case.

>>>>

For MCCS we consider only undirected graphs (and so we treat directed edges in the inputs as being
undirected). For directed graphs, there is more than one notion of connectivity, and it is not clear
which should be selected---the approaches we consider extend easily to weakly connected directed
graphs, but not to the strongly connected case (for which we know of no applications).
